LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment

### 2024-06-12 article/main.tex
apply ACL styling

\documentclass[runningheads,a4paper,11pt]{article}

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{booktabs}
\usepackage[justification=centering,font=scriptsize]{caption}
\usepackage{cite}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\usepackage{inconsolata}
\usepackage[latin1]{inputenc}
\usepackage{interval}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfigure}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{url}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{xstring}

\geometry{a4paper,top=2.5cm,left=2cm,right=2cm,bottom=2cm}

\begin{document}
\title{How Consistent are LLMs in Applying Handcrafted Language Features}
\author{Andrei Olar --- andrei.olar@ubbcluj.ro}
\maketitle
\begin{abstract}
    Large language models are sought for solving an increasing number of
    increasingly diverse tasks. Perhaps naturally one such task is text style
    transfer: the task of changing the style of a text while preserving its
    meaning. Besides the natural approach of fine-tuning a large language model,
    a simpler and cheaper alternative should also be investigated: using
    handcrafted language features to direct the large language model.
\end{abstract}

@@

One final observation before diving into details is that we can use an HLF's
variance on the benchmark dataset to our advantage.
This statistic shows whether the LLM takes the HLF prompts into account enough
for the generated text to fall within the parameters of the benchmark dataset.
Let us denote an HLF computed on a generated text using an HLF prompt with
$HLF_g$.
Similarly denote the average and the variance of the same HLF on the benchmark
dataset with $avg(HLF_b)$ and $var(HLF_b)$, respectively.
If we consistently notice that
\[HLF_g - var(HLF_b) \leq avg(HLF_b) \leq HLF_g + var(HLF_b)\]
then we consider that the LLM follows HLF prompts in a relevant way.

@@

For our experiment we will use state of the art large language models.
We used the Chatbot Arena~\cite{chiang2024chatbot} leaderboard for constructing
our selection.
In the interest of covering more ground, we chose five top performers in the
Chatbot Arena from different vendors.
The final selection is available in Table~\ref{table-llm}.

\begin{table}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \begin{tabular}{@{}lllll@{}}
        \toprule
        Name                    & Parameters  & Context Size & Elo Score & License Type        \\ \toprule
        OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
        Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
        Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
        Meta Llama 3-70B        & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
        Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                                &             &              &           & with Acceptable Use \\
                                &             &              &           & Addendum            \\ \bottomrule
    \end{tabular}
    \caption{Large Language Model Selection}\label{table-llm}
\end{table}

@@

\begin{table}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \begin{tabular}{@{}lllll@{}}
        \toprule
        Name                              & Family           & Domain           & Abstraction     & Style Level\footnotemark \\ \toprule
        total words                       & wordsent         & surface          & very concrete   & lexical                  \\
        total sentences                   & wordsent         & surface          & very concrete   & syntactic                \\ \bottomrule
        total number of unique adjectives & partofspeech     & syntax           & concrete        & semantic                 \\
        total number of unique adjectives & partofspeech     & syntax           & concrete        & syntactic                \\ \bottomrule
        simple type token ratio           & typetokenratio   & lexico-semantics & regular         & pragmatic                \\
        number of verbs per word          & partofspeech     & surface          & regular         & syntactic                \\ \bottomrule
        corrected adjective variation     & lexicalvariation & lexico-semantics & abstract        & lexical                  \\
        corrected verb variation          & lexicalvariation & lexico-semantics & abstract        & lexical                  \\ \bottomrule
        Flesch-Kincaid grade level        & readformula      & surface          & highly abstract & pragmatic                \\
        Kuperman age of aquisition        & worddiff         & lexico-semantics & highly abstract & lexical                  \\ \bottomrule
    \end{tabular}
    \caption{Handcrafted Linguistic Features}\label{table-hlf}
\end{table}
\footnotetext{as described in the figure in~\cite{lugea2023stylistics}, chapter 1, page 7}

Each of these features is well documented~\cite{lftk-2023} barring the need for
a deeper dive here into the subject matter.

@@

We must choose source datasets based upon which we create corpuses for our
experiment.
Our final selection of datasets is listed in Table~\ref{table-ds}.

\begin{table}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \begin{tabular}{@{}lllll@{}}
        \toprule
        Name            & Task                     & Row Count & Content Type & Reference              \\ \toprule
        Yelp Reviews    & Sentiment Classification & 50000     & Reviews      & \cite{yelp2015neurips} \\
        (test split)    & Text Style Transfer      &           &              &                        \\
                        & Text Classification      &           &              &                        \\ \midrule
        CNN / DailyMail & Summarization            & 11490     & News         & \cite{cnndm2015}       \\
        (test split)    & Question Answering       &           & Stories      & \cite{cnndm2017}       \\
                        & Text Generation          &           &              &                        \\ \midrule
    \end{tabular}
    \caption{Source Datasets}\label{table-ds}
\end{table}

@@

@@

\subsection{Can an LLM Follow HLF Instructions?}

The results on the CNN-DailyMail dataset showcased in
Table~\ref{table-prompt-1-cnn-dailymail} provide the most eloquent answer to
this question.
The results on the Yelp dataset are positive, albeit less convincing.
\begin{table}[!ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var            & fkgl                    & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{623.16}}  & \textbf{\underline{24.74}} & \textbf{\underline{51.18}}  & \textbf{\underline{26.68}} & 0.06                      & -0.0                      & \textbf{\underline{0.46}} & \textbf{\underline{1.4}}   & 1.44                    & \textbf{\textit{-1.66}}   \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{1774.0}}  & \textbf{\underline{74.0}}  & \textbf{\underline{158.84}} & \textbf{\underline{81.2}}  & 0.2                       & -0.01                     & \textbf{\underline{1.88}} & \textbf{\underline{4.49}}  & 5.01                    & \textbf{\textit{-4.09}}   \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{985.86}}  & \textbf{\underline{34.52}} & \textbf{\underline{100.36}} & \textbf{\underline{53.39}} & \textbf{\underline{0.52}} & 0.05                      & \textbf{\underline{2.62}} & \textbf{\underline{4.68}}  & -4.17                   & \textbf{\textit{-2.43}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2990.5}}  & \textbf{\underline{106.5}} & \textbf{\underline{320.34}} & \textbf{\underline{159.1}} & \textbf{\underline{1.5}}  & 0.09                      & \textbf{\underline{7.24}} & \textbf{\underline{13.15}} & -12.65                  & \textbf{\textit{-7.13}}   \\ \midrule
            gpt $Diff\_N$         & \textbf{\underline{125.87}}  & 1.46                       & 10.95                       & 10.77                      & 0.02                      & -0.01                     & 0.71                      & 0.81                       & \textbf{\textit{-1.72}} & 0.43                      \\ \midrule
            gpt $Diff\_A$         & \textbf{\underline{327.0}}   & 3.0                        & 29.0                        & 27.0                       & 0.08                      & -0.01                     & 1.82                      & 2.24                       & \textbf{\textit{-5.72}} & 0.44                      \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{1024.78}} & \textbf{\underline{39.67}} & \textbf{\underline{81.58}}  & \textbf{\underline{41.46}} & \textbf{\underline{0.46}} & \textbf{\underline{0.03}} & \textbf{\underline{2.67}} & \textbf{\underline{3.78}}  & 1.4                     & \textbf{\underline{0.14}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{3132.5}}  & \textbf{\underline{120.5}} & \textbf{\underline{246.84}} & \textbf{\underline{132.2}} & \textbf{\underline{1.36}} & \textbf{\underline{0.06}} & \textbf{\underline{7.88}} & \textbf{\underline{11.21}} & 3.9                     & \textbf{\underline{1.03}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{459.45}}  & \textbf{\underline{17.78}} & \textbf{\underline{36.5}}   & \textbf{\underline{19.75}} & \textbf{\underline{0.12}} & \textbf{\underline{0.03}} & \textbf{\underline{1.43}} & \textbf{\underline{2.18}}  & 1.5                     & \textbf{\textit{-0.06}}   \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1363.5}}  & \textbf{\underline{54.0}}  & \textbf{\underline{106.5}}  & \textbf{\underline{60.5}}  & \textbf{\underline{0.36}} & \textbf{\underline{0.09}} & \textbf{\underline{4.33}} & \textbf{\underline{6.38}}  & 7.46                    & \textbf{\textit{-0.11}}   \\ \bottomrule
        \end{tabular}%
    }\caption{CNN Results}\label{table-prompt-1-cnn-dailymail}
\end{table}

For our selection of features, on the CNN corpus of articles, Command-R+ was the
best performer.
GPT scored surprisingly low.

@@

\begin{figure}[ht!]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail_t_word.png}
        \caption{Command-R+\\Total Words}
        \label{fig-command-r-t-word}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail_fkgl.png}
        \caption{GPT\\Flesch-Kincaid Grade Level}
        \label{fig-gpt-fkgl}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail_a_verb_pw.png}
        \caption[center]{Claude3\\Average Verbs per Word}
        \label{fig-llama-simp-ttr}
    \end{minipage}
\end{figure}

\subsection{Context Aware}

@@

\begin{table}[!ht]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var           & fkgl                       & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{718.49}}  & \textbf{\underline{24.13}} & \textbf{\underline{44.43}}  & \textbf{\underline{23.43}} & \textbf{\underline{0.4}}  & 0.03                      & 0.94                      & \textbf{\underline{0.77}} & 1.2                        & 0.07                      \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2345.54}} & \textbf{\underline{90.18}} & \textbf{\underline{148.36}} & \textbf{\underline{63.6}}  & \textbf{\underline{1.18}} & 0.07                      & 1.36                      & \textbf{\underline{2.55}} & 3.33                       & 0.52                      \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{785.6}}   & \textbf{\underline{25.8}}  & \textbf{\underline{60.5}}   & \textbf{\underline{41.6}}  & \textbf{\underline{0.41}} & \textbf{\underline{0.05}} & \textbf{\underline{1.95}} & \textbf{\underline{2.67}} & -4.62                      & \textbf{\textit{-1.94}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2512.0}}  & \textbf{\underline{81.5}}  & \textbf{\underline{210.34}} & \textbf{\underline{125.7}} & \textbf{\underline{1.25}} & \textbf{\underline{0.09}} & \textbf{\underline{5.84}} & \textbf{\underline{8.05}} & -9.46                      & \textbf{\textit{-5.82}}   \\ \midrule
            gpt $Diff\_N$         & 47.8                         & 5.18                       & 6.13                        & -0.13                      & 0.02                      & 0.0                       & 0.05                      & 0.3                       & 3.06                       & -0.27                     \\ \midrule
            gpt $Diff\_A$         & 77.0                         & 12.5                       & 13.0                        & -4.0                       & 0.04                      & 0.0                       & -0.17                     & 0.77                      & 8.45                       & -0.16                     \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{263.51}}  & 5.35                       & \textbf{\underline{25.08}}  & \textbf{\underline{17.37}} & \textbf{\textit{-0.09}}   & -0.01                     & \textbf{\underline{1.74}} & \textbf{\underline{1.42}} & \textbf{\underline{10.46}} & \textbf{\underline{1.56}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{896.0}}   & 20.5                       & \textbf{\underline{86.0}}   & \textbf{\underline{60.6}}  & \textbf{\textit{-0.21}}   & -0.03                     & \textbf{\underline{5.45}} & \textbf{\underline{4.95}} & \textbf{\underline{31.29}} & \textbf{\underline{5.67}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{376.0}}   & \textbf{\underline{15.63}} & \textbf{\underline{38.63}}  & 15.74                      & \textbf{\underline{0.24}} & \textbf{\underline{0.06}} & 1.69                      & \textbf{\underline{2.91}} & 0.31                       & -0.3                      \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1088.5}}  & \textbf{\underline{45.0}}  & \textbf{\underline{113.0}}  & 41.0                       & \textbf{\underline{0.65}} & \textbf{\underline{0.18}} & 3.53                      & \textbf{\underline{8.56}} & 0.27                       & -0.68                     \\ \bottomrule
        \end{tabular}%
    }
    \caption{prompt 2 - CNN Results\\Input Outside Corpus}
    \label{table-prompt-2-cnn-dailymail}
\end{table}

@@

\begin{figure}[ht!]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail_t_word.png}
        \caption{GPT\\Total Words}
        \label{fig-p2-gpt-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail_simp_ttr.png}
        \caption{Command-R+\\Simple TTR}
        \label{fig-p2-command-r-simpttr}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Gemini\\Kuperman Age of Aquisition}
        \label{fig-p2-gemini-a-kup-pw}
    \end{minipage}
\end{figure}

@@

\bibliographystyle{plain}
\bibliography{references}
\end{document}

>>>>

\pdfoutput=1

\documentclass[11pt]{article}
\usepackage[review]{acl}

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{array}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{balance}
\usepackage{booktabs}
\usepackage[justification=centering]{caption}
\usepackage{comment}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{inconsolata}
\usepackage[utf8]{inputenc}
\usepackage{interval}
\usepackage{microtype}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{setspace}
\usepackage{subfigure}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{url}
\usepackage{verbatim}
\usepackage{xcolor}
\usepackage{xstring}

\title{LLM Output Compliance with Handcrafted Linguistic Features --- An Experiment}
\author{Andrei Olar\\
Universitatea Babeș-Bolyai, Cluj-Napoca, România\\
\texttt{andrei.olar@ubbcluj.ro}\\}

\begin{document}
\maketitle
\begin{abstract}
    Large language models are sought for solving an increasing number of
    increasingly diverse tasks. Perhaps naturally one such task is text style
    transfer: the task of changing the style of a text while preserving its
    meaning. Besides the natural approach of fine-tuning a large language model,
    a simpler and cheaper alternative should also be investigated: using
    handcrafted language features to direct the large language model.
\end{abstract}

@@

@@

For our experiment we will use state of the art large language models.
We used the Chatbot Arena~\cite{chiang2024chatbot} leaderboard for constructing
our selection.
In the interest of covering more ground, we chose five top performers in the
Chatbot Arena from different vendors.
The final selection is available in Table~\ref{table-llm}. The identifier

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            ID          & Name                    & Parameters  & Context Size & Elo Score & License Type        \\ \toprule
            gpt         & OpenAI GPT-4o           & undisclosed & 128000       & 1287      & Proprietary         \\
            gemini      & Google Gemini 1.5 Pro   & undisclosed & 1048576      & 1268      & Proprietary         \\
            claude3     & Anthropic Claude 3 Opus & undisclosed & 200000       & 1248      & Proprietary         \\
            llama3\_70b & Meta Llama 3-70B        & 70 Billion  & 8000         & 1208      & Llama 3 Community   \\
            command\_r  & Cohere Command R+       & 104 Billion & 128000       & 1189      & CC-BY-NC 4.0        \\
                        &                         &             &              &           & with Acceptable Use \\
                        &                         &             &              &           & Addendum            \\ \bottomrule
        \end{tabular}%
    }
    \caption{Large Language Model Selection}\label{table-llm}
\end{table*}

The ID of the LLM is used as the reference throughout figures and tables.

@@

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}llllll@{}}
            \toprule
            LFTK ID         & Name                              & Family           & Domain           & Abstraction     & Style Level\footnotemark \\ \toprule
            t\_word         & total words                       & wordsent         & surface          & very concrete   & lexical                  \\
            t\_sent         & total sentences                   & wordsent         & surface          & very concrete   & syntactic                \\ \bottomrule
            n\_uverb        & total number of unique adjectives & partofspeech     & syntax           & concrete        & semantic                 \\
            n\_uadj         & total number of unique adjectives & partofspeech     & syntax           & concrete        & syntactic                \\ \bottomrule
            simp\_ttr       & simple type token ratio           & typetokenratio   & lexico-semantics & regular         & pragmatic                \\
            a\_verb\_pw     & number of verbs per word          & partofspeech     & surface          & regular         & syntactic                \\ \bottomrule
            corr\_adj\_var  & corrected adjective variation     & lexicalvariation & lexico-semantics & abstract        & lexical                  \\
            corr\_verb\_var & corrected verb variation          & lexicalvariation & lexico-semantics & abstract        & lexical                  \\ \bottomrule
            fkgl            & Flesch-Kincaid grade level        & readformula      & surface          & highly abstract & pragmatic                \\
            a\_kup\_pw      & Kuperman age of aquisition        & worddiff         & lexico-semantics & highly abstract & lexical                  \\ \bottomrule
        \end{tabular}%
    }
    \caption{Handcrafted Linguistic Features}\label{table-hlf}
\end{table*}
\footnotetext{as described in the figure in~\cite{lugea2023stylistics}, chapter 1, page 7}

Each of these features is well documented~\cite{lftk-2023}, barring the need for
an extended description here.
The LFTK ID is used throughout tables and figures to refer to a specific HLF.

@@

The experiment design rests upon measuring HLFs on corpuses of texts and
computing statistics.
LLMs also make use of examples extracted from a corpus to guide text generation.
We obtain a corpus from a dataset.
Our final selection of datasets is listed in Table~\ref{table-ds}.

\begin{table*}[ht]
    \setlength\tabcolsep{6pt}
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{@{}lllll@{}}
            \toprule
            Name            & Task                     & Number of Samples & Content Type & Reference              \\ \toprule
            Yelp Reviews    & Sentiment Classification & 50000             & Reviews      & \cite{yelp2015neurips} \\
            (test split)    & Text Style Transfer      &                   &              &                        \\
                            & Text Classification      &                   &              &                        \\ \midrule
            CNN / DailyMail & Summarization            & 11490             & News         & \cite{cnndm2015}       \\
            (test split)    & Question Answering       &                   & Stories      & \cite{cnndm2017}       \\
                            & Text Generation          &                   &              &                        \\ \midrule
        \end{tabular}%
    }
    \caption{Source Datasets}\label{table-ds}
\end{table*}

@@

Lastly, it should be noted that each HLF has an independent value range.
The number of total words ranges from small numbers into the hundreds or more,
while the corrected verb variation is always a small number.
The area and the Euclidian norm are calculated using the raw values of each HLF.
That makes the values in each table column incomparable to the values in another
table column.
Because we don't show the measure of the difference between the baseline and the
result, but the relative closeness to a target based on that measure, comparing
values from the same column is also ill-advised.

@@

\subsection{HLF Instruction Impact}

The results on the corpus containing CNN articles showcased in
Table~\ref{table-prompt-1-cnn-dailymail} shows that most LLMs take into account
instructions concerning the linguistic features of their output.

The results on the review corpus generated from the Yelp dataset are similarly
significant, but the HLF instructions determine outcomes that are further away
from the target.

\begin{table*}[htp]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var            & fkgl                    & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{623.16}}  & \textbf{\underline{24.74}} & \textbf{\underline{51.18}}  & \textbf{\underline{26.68}} & 0.06                      & -0.0                      & \textbf{\underline{0.46}} & \textbf{\underline{1.4}}   & 1.44                    & \textbf{\textit{-1.66}}   \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{1774.0}}  & \textbf{\underline{74.0}}  & \textbf{\underline{158.84}} & \textbf{\underline{81.2}}  & 0.2                       & -0.01                     & \textbf{\underline{1.88}} & \textbf{\underline{4.49}}  & 5.01                    & \textbf{\textit{-4.09}}   \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{985.86}}  & \textbf{\underline{34.52}} & \textbf{\underline{100.36}} & \textbf{\underline{53.39}} & \textbf{\underline{0.52}} & 0.05                      & \textbf{\underline{2.62}} & \textbf{\underline{4.68}}  & -4.17                   & \textbf{\textit{-2.43}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2990.5}}  & \textbf{\underline{106.5}} & \textbf{\underline{320.34}} & \textbf{\underline{159.1}} & \textbf{\underline{1.5}}  & 0.09                      & \textbf{\underline{7.24}} & \textbf{\underline{13.15}} & -12.65                  & \textbf{\textit{-7.13}}   \\ \midrule
            gpt $Diff\_N$         & \textbf{\underline{125.87}}  & 1.46                       & 10.95                       & 10.77                      & 0.02                      & -0.01                     & 0.71                      & 0.81                       & \textbf{\textit{-1.72}} & 0.43                      \\ \midrule
            gpt $Diff\_A$         & \textbf{\underline{327.0}}   & 3.0                        & 29.0                        & 27.0                       & 0.08                      & -0.01                     & 1.82                      & 2.24                       & \textbf{\textit{-5.72}} & 0.44                      \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{1024.78}} & \textbf{\underline{39.67}} & \textbf{\underline{81.58}}  & \textbf{\underline{41.46}} & \textbf{\underline{0.46}} & \textbf{\underline{0.03}} & \textbf{\underline{2.67}} & \textbf{\underline{3.78}}  & 1.4                     & \textbf{\underline{0.14}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{3132.5}}  & \textbf{\underline{120.5}} & \textbf{\underline{246.84}} & \textbf{\underline{132.2}} & \textbf{\underline{1.36}} & \textbf{\underline{0.06}} & \textbf{\underline{7.88}} & \textbf{\underline{11.21}} & 3.9                     & \textbf{\underline{1.03}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{459.45}}  & \textbf{\underline{17.78}} & \textbf{\underline{36.5}}   & \textbf{\underline{19.75}} & \textbf{\underline{0.12}} & \textbf{\underline{0.03}} & \textbf{\underline{1.43}} & \textbf{\underline{2.18}}  & 1.5                     & \textbf{\textit{-0.06}}   \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1363.5}}  & \textbf{\underline{54.0}}  & \textbf{\underline{106.5}}  & \textbf{\underline{60.5}}  & \textbf{\underline{0.36}} & \textbf{\underline{0.09}} & \textbf{\underline{4.33}} & \textbf{\underline{6.38}}  & 7.46                    & \textbf{\textit{-0.11}}   \\ \bottomrule
        \end{tabular}%
    }\caption{CNN Results}\label{table-prompt-1-cnn-dailymail}
\end{table*}

@@

\begin{figure*}[htp]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-command_r-cnn_dailymail/prompt_1-command_r-cnn_dailymail_t_word.png}
        \caption{Command-R+\\Total Words}
        \label{fig-command-r-t-word}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-gpt-cnn_dailymail/prompt_1-gpt-cnn_dailymail_fkgl.png}
        \caption{GPT\\Flesch-Kincaid Grade Level}
        \label{fig-gpt-fkgl}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_1/prompt_1-claude3-cnn_dailymail/prompt_1-claude3-cnn_dailymail_a_verb_pw.png}
        \caption[center]{Claude3\\Average Verbs per Word}
        \label{fig-llama-simp-ttr}
    \end{minipage}
\end{figure*}

\subsection{HLF Instructions and Context Awareness}

@@

\begin{table*}[hpb]
    \centering
    \resizebox{\textwidth}{!}{%
        \begin{tabular}{lllllllllll}
            model                 & t\_word                      & t\_sent                    & n\_uverb                    & n\_uadj                    & simp\_ttr                 & a\_verb\_pw               & corr\_adj\_var            & corr\_verb\_var           & fkgl                       & a\_kup\_pw                \\
            \toprule
            claude3 $Diff\_N$     & \textbf{\underline{718.49}}  & \textbf{\underline{24.13}} & \textbf{\underline{44.43}}  & \textbf{\underline{23.43}} & \textbf{\underline{0.4}}  & 0.03                      & 0.94                      & \textbf{\underline{0.77}} & 1.2                        & 0.07                      \\ \midrule
            claude3 $Diff\_A$     & \textbf{\underline{2345.54}} & \textbf{\underline{90.18}} & \textbf{\underline{148.36}} & \textbf{\underline{63.6}}  & \textbf{\underline{1.18}} & 0.07                      & 1.36                      & \textbf{\underline{2.55}} & 3.33                       & 0.52                      \\ \midrule
            gemini $Diff\_N$      & \textbf{\underline{785.6}}   & \textbf{\underline{25.8}}  & \textbf{\underline{60.5}}   & \textbf{\underline{41.6}}  & \textbf{\underline{0.41}} & \textbf{\underline{0.05}} & \textbf{\underline{1.95}} & \textbf{\underline{2.67}} & -4.62                      & \textbf{\textit{-1.94}}   \\ \midrule
            gemini $Diff\_A$      & \textbf{\underline{2512.0}}  & \textbf{\underline{81.5}}  & \textbf{\underline{210.34}} & \textbf{\underline{125.7}} & \textbf{\underline{1.25}} & \textbf{\underline{0.09}} & \textbf{\underline{5.84}} & \textbf{\underline{8.05}} & -9.46                      & \textbf{\textit{-5.82}}   \\ \midrule
            gpt $Diff\_N$         & 47.8                         & 5.18                       & 6.13                        & -0.13                      & 0.02                      & 0.0                       & 0.05                      & 0.3                       & 3.06                       & -0.27                     \\ \midrule
            gpt $Diff\_A$         & 77.0                         & 12.5                       & 13.0                        & -4.0                       & 0.04                      & 0.0                       & -0.17                     & 0.77                      & 8.45                       & -0.16                     \\ \midrule
            command\_r $Diff\_N$  & \textbf{\underline{263.51}}  & 5.35                       & \textbf{\underline{25.08}}  & \textbf{\underline{17.37}} & \textbf{\textit{-0.09}}   & -0.01                     & \textbf{\underline{1.74}} & \textbf{\underline{1.42}} & \textbf{\underline{10.46}} & \textbf{\underline{1.56}} \\ \midrule
            command\_r $Diff\_A$  & \textbf{\underline{896.0}}   & 20.5                       & \textbf{\underline{86.0}}   & \textbf{\underline{60.6}}  & \textbf{\textit{-0.21}}   & -0.03                     & \textbf{\underline{5.45}} & \textbf{\underline{4.95}} & \textbf{\underline{31.29}} & \textbf{\underline{5.67}} \\ \midrule
            llama3\_70b $Diff\_N$ & \textbf{\underline{376.0}}   & \textbf{\underline{15.63}} & \textbf{\underline{38.63}}  & 15.74                      & \textbf{\underline{0.24}} & \textbf{\underline{0.06}} & 1.69                      & \textbf{\underline{2.91}} & 0.31                       & -0.3                      \\ \midrule
            llama3\_70b $Diff\_A$ & \textbf{\underline{1088.5}}  & \textbf{\underline{45.0}}  & \textbf{\underline{113.0}}  & 41.0                       & \textbf{\underline{0.65}} & \textbf{\underline{0.18}} & 3.53                      & \textbf{\underline{8.56}} & 0.27                       & -0.68                     \\ \bottomrule
        \end{tabular}%
    }
    \caption{prompt 2 - CNN Results\\Input Outside Corpus}
    \label{table-prompt-2-cnn-dailymail}
\end{table*}

@@

\begin{figure*}[hpb]
    \centering
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gpt-cnn_dailymail/prompt_2-gpt-cnn_dailymail_t_word.png}
        \caption{GPT\\Total Words}
        \label{fig-p2-gpt-twords}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-command_r-cnn_dailymail/prompt_2-command_r-cnn_dailymail_simp_ttr.png}
        \caption{Command-R+\\Simple TTR}
        \label{fig-p2-command-r-simpttr}
    \end{minipage}
    \hfill
    \begin{minipage}{0.32\textwidth}
        \includegraphics[width=\linewidth]{plots/prompt_2/prompt_2-gemini-cnn_dailymail/prompt_2-gemini-cnn_dailymail_a_kup_pw.png}
        \caption[center]{Gemini\\Kuperman Age of Aquisition}
        \label{fig-p2-gemini-a-kup-pw}
    \end{minipage}
\end{figure*}

@@

\bibliography{references}

\end{document}
